Probabilistic Policy Violation Detection with IPFWD

### 2017-02-06 paper/main.tex
Add graphs to paper

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

% Explain different systems
Tests were run on three different systems and five different network cards.

% Isilon 40G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{Isilon OneFS 40Gb System} \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Xeon\textsuperscript{\textregistered}\ CPU @ 2.20GHz \\
 MEM &  64Gb \\
 NIC &  Ethernet 40Gbase-T \\ 
 \hline
\end{tabular}\\\\

% Isilon 10G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{Isilon OneFS 10Gb System} \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Xeon\textsuperscript{\textregistered}\ CPU @ 2.20GHz \\
 MEM &  64Gb RAM \\
 NIC &  Ethernet 10Gbase-T \\ 
 \hline
\end{tabular} \\\\

% WWU 10G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{ WWU 10Gb System } \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Core\texttrademark\ i7-2600 CPU @ 3.4GHz \\
 MEM &  16Gb \\ 
 NIC &  ??? \\ 
 \hline
\end{tabular} \\\\

% WWU 1G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{ WWU 1Gb System } \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Core\texttrademark\ i7-2600 CPU @ 3.4GHz \\
 MEM &  16Gb \\
 NIC &  Ethernet 1000baseT \\ 
 \hline
\end{tabular} \\\\

% Virtualized 10G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{ Virtualized 10G System } \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  1 x64 Intel\textsuperscript{\textregistered}\ Xeon\textsuperscript{\textregistered}\ CPU @ 1.80GHz \\
 MEM &  512Mb \\
 NIC &  Ethernet 10Gbase-T \\ 
 \hline
\end{tabular} \\\\

@@

% Explain tests
The test type UDP\_STREAM was chosen over TCP\_STREAM for simplicity and to
preserve CPU cycles for IPFW. Raw network throughput and CPU performance is the
target metric, which can be difficult to assess with TCP. (REFERENCE)

@@

CPU utilization measurement is the most difficult parameter to measure in these
tests. There are many factors that can account for variability between tests
and jitter in the results.

\section{Results}

% Show results

@@

In CPU bound systems, IPFWD reduces the number of cycles it takes to process
each packet, allowing more packets to be processed in the same time and
increasing throughput. This is shown most clearly in the Virtualized system
tests, which have the weakest CPU but 10Gb Ethernet NICs. This finding is also
apparent in the 40Gb Isilon system.

In NIC throughput bound systems, reducing the number of CPU cycles to process
packets will not increase throughput. However, IPFWD still reduces CPU load
which allows more cycles to be dedicated to other system processes.

@@

% Machine learning firewalls
\blindtext

@@

\blindtext

@@

\appendices
\section{Proof of the First Zonklar Equation}
Some text for the appendix.

@@

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{picture}}]{John Doe}
\blindtext
\end{IEEEbiography}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

% Explain different systems
Tests were run on three platforms and five different network cards, resulting
in five different systems. The most important parameters to our tests are CPU,
NIC, and ENV. Descriptions of each system are given in the tables below:\\

% Isilon 40G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{Isilon OneFS 40Gb System} \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Xeon\textsuperscript{\textregistered}\ CPU @ 2.20GHz \\
 MEM &  64Gb \\
 NIC &  Ethernet 40Gbase-T \\ 
 ENV &  Physical \\ 
 \hline
\end{tabular}\\\\

% Isilon 10G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{Isilon OneFS 10Gb System} \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Xeon\textsuperscript{\textregistered}\ CPU @ 2.20GHz \\
 MEM &  64Gb RAM \\
 NIC &  Ethernet 10Gbase-T \\ 
 ENV &  Physical \\ 
 \hline
\end{tabular} \\\\

% WWU 10G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{ WWU 10Gb System } \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Core\texttrademark\ i7-2600 CPU @ 3.4GHz \\
 MEM &  16Gb \\ 
 NIC &  ??? \\ 
 ENV &  Physical \\ 
 \hline
\end{tabular} \\\\

% WWU 1G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{ WWU 1Gb System } \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Core\texttrademark\ i7-2600 CPU @ 3.4GHz \\
 MEM &  16Gb \\
 NIC &  Ethernet 1000baseT \\ 
 ENV &  Physical \\ 
 \hline
\end{tabular} \\\\

% Virtualized 10G
\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{ Virtualized 10G System } \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  1 x64 Intel\textsuperscript{\textregistered}\ Xeon\textsuperscript{\textregistered}\ CPU @ 1.80GHz \\
 MEM &  512Mb \\
 NIC &  Ethernet 10Gbase-T \\ 
 ENV &  Hypervisor \\ 
 \hline
\end{tabular} \\\\

@@

  % Explain tests
  The test type UDP\_STREAM was chosen over TCP\_STREAM for simplicity and to
  preserve CPU cycles for IPFW. Raw network throughput and CPU performance is
  the target metric, which can be difficult to assess with TCP.

@@

  \subsection{CPU Measurement}

  CPU utilization measurement is the most difficult parameter to measure in
  these tests. There are many factors that can account for variability between
  tests and jitter in the results. The Netperf manual describes these
  challenges and the variety of techniques used on different systems.

  Netperf was run in single threaded mode, which explains why throughput wasn't
  closer to the maximum throughput for the NIC on each system. The FreeBSD
  network stack allows multithreaded packet processing by utilizing multiple
  queues. Since we're indirectly testing the performance of IPFW through
  Netperf, there are two different CPU measurements to account for: kernel time
  and user time. Since IPFW runs in the kernel, it's CPU time is classified as
  kernel time.

  Netperf was able to measure CPU utilization on the Virtualized and WWU
  systems, but didn't work on the Isilon systems. Instead, ps was used on those
  systems.  These tests are comparable since both measured total system CPU
  utilization

% Show results graphs, explain axises, etc
\section{Results}

  % throughput/CPU
  \subsection{Throughput / CPU}
  These graphs show network throughput divided by CPU utilization for each system. Higher values mean that the CPU time required to process packets is lower.

  \begin{center}
  \includegraphics[width=0.45\textwidth]{toc_isilon40}
  \includegraphics[width=0.45\textwidth]{toc_isilon10}
  \includegraphics[width=0.45\textwidth]{toc_wwu1}
  \includegraphics[width=0.45\textwidth]{toc_virtual10}
  \end{center}

  %  throughput & CPU
  \subsection{Throughput \& CPU}
  These graphs show the interaction between CPU utilization and network throughput for each system with respect to IPFWD's acceptance probability. The dashed lines are CPU utilization, solid is network throughput in Mb/second. Higher acceptance probability means a greater chance that a given packet is immediately accepted without further processing.

  \begin{center}
  \includegraphics[width=0.45\textwidth]{isilon40_cpu}
  \includegraphics[width=0.45\textwidth]{isilon10_cpu}
  \includegraphics[width=0.45\textwidth]{wwu1_cpu}
  \includegraphics[width=0.45\textwidth]{virtual10_cpu}
  \end{center}

@@

  In CPU bound systems, IPFWD reduces the number of cycles it takes to process
  each packet, allowing more packets to be processed in the same time and
  increasing throughput. This is shown most clearly in the Virtualized system
  tests, which have the weakest CPU but 10Gb Ethernet NICs. Regardless of test
  type, the receiving system is always at 100\% CPU utilization. However, as
  the probability to accept increases in IPFWD the throughput also increases.
  This clearly shows that IPFWD decreases the CPU load required to process
  incoming traffic.

  In NIC throughput bound systems, reducing the number of CPU cycles to process
  packets will not increase throughput. However, IPFWD still reduces CPU load
  which allows more cycles to be dedicated to other system processes. This is
  more difficult to see in the test results, particularly since the CPU
  measurement tools are inherently imprecise and difficult to compare between
  systems.

@@

% Machine learning firewalls

@@

@@

\appendices
\section{Additional Figures}
Some text for the appendix.

@@

% http://www.netperf.org/svn/netperf2/tags/netperf-2.7.0/doc/netperf.html#CPU-Utilization

@@
